---
title: "STA305 A1"
author: "Terence Chan"
date: "27/01/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Part A.

### 1.
```{r}
set.seed(1366)
```

### 2.

## Treatment S

```{r}
dat_S <- round(rnorm(8, 5, 2),3)
dat_S
```

### 3.

## Treatment T

```{r}
dat_T <- round(rnorm(8, 7, 2),3)
dat_T
```

### 4.

```{r}
dat_both <- data.frame(dat_S,dat_T)
dat_both
```

#### Part B

# Completely Randomized Design

```{r}
s <- c(dat_S)
t <- c(dat_T)
s_t <- c(s, t)
m <- mean(s - t)
N <-choose(16,8)
result_N1 <- numeric(N)
assmt <- combn(1:16,8)
for (i in 1:N)
+ {result_N1[i] <- mean(s_t[assmt[,i]]) - mean(s_t[-assmt[,i]])}

t <- mean(result_N1)
pvalue1 <- sum(abs(result_N1 - t) >= abs(m-t))/N
pvalue1
```

There are 16 observations in total, 8 observations of 2 variables. The distribution approximately follows a normal distribution. The two-sided p-value is roughly 0.22. Since the p-value is greater than 5%, we fail to reject the null hypothesis.


```{r}
graph <- hist(result_N1,xlab = "Mean Difference", main = "Randomization Test of
              Completely Randomized Design")
abline(v = pvalue1, col = "red")
```


# Randomized Paired Design


```{r}
a <- dat_both$dat_S - dat_both$dat_T
dat2 <- data.frame(dat_both, a)   
dat2
```


```{r}
treatment <- 2^(8) 
result_N2 <- numeric(treatment) 
b <- list(c(-1,1)) 
c <- expand.grid(rep(b, 8)) 

for(i in 1:treatment){
result_N2[i] <- mean(as.numeric(c[i,])*a)
}
```


```{r}
pvalue2 <- sum(result_N2 <= a)/treatment
pvalue2
```

```{r}
hist(result_N2, xlab="Mean Difference",main="Randomization Test of 
     Randomized Paired Design")
abline(v = pvalue2, col="red")
```

The two-sided p-value of the completely randomized design is 0.43 and the value for the randomized paired design is 0.39 which indicates that there is a slgiht discrepancy due to the difference in assignment treatments for both designs. Furthermore, this indicates that the null hypothesis cannot be rejected due to a p-value that is greater than 5%


#### Part C.

# Completely Ranodomized Design

```{r}
t1 <- t.test(s,t,var.equal = TRUE, alternative = "less")
t1
```

# Randomized Paired Design

```{r}
t2 <- t.test(dat_both$dat_S, dat_both$dat_T, paired = TRUE, alternative = 'less')
t2
```

### (i).

The p-value of the completely randomized design is 0.21 and the paired design is 0.24 which are both greater than 5%. This indicates that the null hypothesis cannot be rejected.

### (ii).

The assumptions for the t-test are that the data is randomly generated and that the means of the distribution follows a normal distribution. The data was generated from a random seed simulation in part A. Furthermore, the test consists of an increasing number of independent random variables, therefore by the central limit theorem, the distirbution of the means follows a normal distribution, therefore both assumptions are satisfied. 

### (iii.)



The two-sided p-value for the completely randomized design for part B and C is 0.22 and 0.21 respectively. The p-value for the randomized paired design for part B and C is 0.22 and 0.24 respectively. There is a slight discrepancy due to the treatment assignments. Therefore the results of the t-test agree with the results of the randomization test in part B.





